Gafo-cc data processing

### 2022-12-06 analysis/gafo-cc-data-processing.Rmd
add more data

```{r demographics}
raw_demographics_leipzig <- bind_rows(
  read_xlsx("../../../../../Cloud/QuantEx/Gafo-cc/docs/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
  )

@@

@@

mdata <- data%>%
  filter(community == "leipzig" | community == "akure",
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(screen,touchscreen.x, household, children, younger_children, sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, touchscreen.y , os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site))

@@

>>>>

```{r demographics}
raw_demographics_leipzig <- bind_rows(
  #read_xlsx("../../../../../Cloud/QuantEx/Gafo-cc/docs/", sheet = 1)
  read_xlsx("../../raw_data/gafo-cc/leipzig/Gafo-cc-leipzig-participants.xlsx", sheet = 1)
  )

@@

```{r}
data%>%
  filter(community == "leipzig")%>%
  mutate(age_group = substr(ageinyears, 1,1))%>%
  group_by(screen, age_group)%>%
  summarise(n = n_distinct(subjid))
```

@@

mdata <- data%>%
  filter(community != "chimfunshi",
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site, `phone number in DB`,`location` ))

@@

write_csv(mdata, file = "../model/model_data/gafo-cc-model-data.csv")
